\section{Launching the Open Physics Education
Network}\label{launching-the-open-physics-education-network}

\subsection{A New Home for Open Physics Course
Materials}\label{a-new-home-for-open-physics-course-materials}

We are excited to announce the launch of the Open Physics Education
Network---a new home for open, accessible, and collaborative physics
education!

\subsection{Why Open?}\label{why-open}

The Open Physics Education Network was created to organize and support
the development of open, high-quality, and accessible resources for
physics and computational science. Our mission is to lower barriers to
learning and empower students, educators, and contributors everywhere.

\subsection{What's Here Now?}\label{whats-here-now}

\begin{itemize}
\tightlist
\item
  A modern, accessible, and WCAG-compliant site design
\item
  News, updates, and community information
\item
  A growing set of open courses, starting with
  \href{https://dannycaballero.info/modern-classical-mechanics/}{Modern
  Classical Mechanics}
\item
  Clear ways to get involved and contribute
\end{itemize}

\subsection{What's Next?}\label{whats-next}

We're actively working to expand Open Physics Ed with new courses and
resources, including: - Introductory Mechanics - Introductory
Electromagnetism - Advanced Electromagnetism - Mathematical Methods -
Introduction to Computational and Data Science - Introduction to Machine
Learning for Undergraduate Physics Research - (Coming soon) Quantum
Physics, Modern Physics, and Statistical Mechanics

\subsection{Get Involved}\label{get-involved}

The Open Physics Education Network is open source and welcomes
contributions from everyone. Suggest new content, report issues, or
submit pull requests on our
\href{https://github.com/open-physics-ed/open-physics-ed-org.github.io}{GitHub
repository}.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Open Physics Ed is just getting started. Join us as we build a more
accessible, equitable future for physics education!
