\section{oerforge.export\_all --- Export All Content and
Assets}\label{oerforge.export_all-export-all-content-and-assets}

\subsection{Overview}\label{overview}

\texttt{oerforge.export\_all} provides utilities for exporting all site
content, assets, and resources from the OERForge project for deployment,
backup, or external use. It is designed to help new users and
programmers automate the process of collecting and packaging all
generated files, static assets, and documentation in a consistent
manner.

\begin{itemize}
\tightlist
\item
  \textbf{Exports all generated HTML, assets, and documentation}
\item
  \textbf{Supports copying to external directories or archives}
\item
  \textbf{Ensures directory structure and file integrity}
\item
  \textbf{Integrates with build and deployment workflows}
\item
  \textbf{Robust logging and error handling}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Functions}\label{functions}

\subsubsection{export\_all\_content(output\_dir=`export',
include\_assets=True,
include\_docs=True)}\label{export_all_contentoutput_direxport-include_assetstrue-include_docstrue}

Export all site content, assets, and documentation to a target
directory.

\textbf{Parameters} - \texttt{output\_dir} (str): Target directory for
export (default: `export'). - \texttt{include\_assets} (bool): Whether
to include static assets (CSS, JS, images). - \texttt{include\_docs}
(bool): Whether to include documentation files.

\textbf{Returns} - \texttt{None}

\textbf{Notes} - Creates target directories if they do not exist. -
Overwrites files in the export directory each time it is called. - Logs
all operations and errors for auditing.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{copy\_directory(src, dst)}\label{copy_directorysrc-dst}

Recursively copy a directory and its contents to a target location.

\textbf{Parameters} - \texttt{src} (str): Source directory path. -
\texttt{dst} (str): Destination directory path.

\textbf{Returns} - \texttt{None}

\textbf{Notes} - Creates destination directory if missing. - Overwrites
files in the destination.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{export\_database(db\_path,
output\_dir)}\label{export_databasedb_path-output_dir}

Export the SQLite database file to the export directory.

\textbf{Parameters} - \texttt{db\_path} (str): Path to the SQLite
database file. - \texttt{output\_dir} (str): Target directory for
export.

\textbf{Returns} - \texttt{None}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{export\_reports(reports\_dir,
output\_dir)}\label{export_reportsreports_dir-output_dir}

Export all accessibility and build reports to the export directory.

\textbf{Parameters} - \texttt{reports\_dir} (str): Source directory for
reports. - \texttt{output\_dir} (str): Target directory for export.

\textbf{Returns} - \texttt{None}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{main()}\label{main}

CLI entry point. Parses arguments and runs export operations as needed.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Logging}\label{logging}

All major operations and errors are logged for debugging and auditing.

\subsection{Error Handling}\label{error-handling}

Robust error handling is implemented for file I/O and directory
operations. All failures are logged with context.

\subsection{Example Usage}\label{example-usage}

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ oerforge }\ImportTok{import}\NormalTok{ export\_all}
\NormalTok{export\_all.export\_all\_content(output\_dir}\OperatorTok{=}\StringTok{\textquotesingle{}export\textquotesingle{}}\NormalTok{, include\_assets}\OperatorTok{=}\VariableTok{True}\NormalTok{, include\_docs}\OperatorTok{=}\VariableTok{True}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{License}\label{license}

See LICENSE in the project root.
