\section{oerforge.verify --- Accessibility Verification and
Reporting}\label{oerforge.verify-accessibility-verification-and-reporting}

\subsection{Overview}\label{overview}

\texttt{oerforge.verify} provides tools for automated accessibility
checking, badge generation, and reporting for static HTML sites. It
integrates with \href{https://pa11y.org/}{Pa11y} for WCAG compliance
checks, manages results in a SQLite database, and generates visual
badges and detailed reports for each page. This module is designed for
new users, educators, and developers seeking robust accessibility
workflows in open educational resources.

\begin{itemize}
\tightlist
\item
  \textbf{Automated accessibility checks (WCAG AA/AAA) using Pa11y}
\item
  \textbf{Badge and report generation for each HTML page}
\item
  \textbf{Database integration for tracking results}
\item
  \textbf{Jinja2-based report rendering}
\item
  \textbf{Robust logging and error handling}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Functions}\label{functions}

\subsubsection{load\_pa11y\_config(yml\_path='\_content.yml')}\label{load_pa11y_configyml_path_content.yml}

Load Pa11y configuration and logo info from YAML and JSON files.

\textbf{Parameters} - \texttt{yml\_path} (str): Path to the YAML config
file.

\textbf{Returns} - \texttt{dict}: Parsed configuration dictionary.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{run\_pa11y\_on\_file(html\_path, config\_path=None,
wcag\_level=`AA')}\label{run_pa11y_on_filehtml_path-config_pathnone-wcag_levelaa}

Run Pa11y accessibility checks on a single HTML file.

\textbf{Parameters} - \texttt{html\_path} (str): Path to the HTML file.
- \texttt{config\_path} (str, optional): Path to Pa11y config file. -
\texttt{wcag\_level} (str): WCAG level (`AA' or `AAA').

\textbf{Returns} - \texttt{list{[}dict{]}} or \texttt{None}: Parsed
Pa11y JSON results, or None on error.

\textbf{Notes} - Handles errors robustly, logs issues, and attempts to
parse output even on failure.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{get\_content\_id\_for\_file(html\_path,
conn)}\label{get_content_id_for_filehtml_path-conn}

Get the content ID for a given HTML file from the database.

\textbf{Parameters} - \texttt{html\_path} (str): Path to the HTML file.
- \texttt{conn} (sqlite3.Connection): Database connection.

\textbf{Returns} - \texttt{int} or \texttt{None}: Content ID if found,
else None.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{store\_accessibility\_result(content\_id, pa11y\_json,
badge\_html, wcag\_level, error\_count, warning\_count, notice\_count,
conn=None)}\label{store_accessibility_resultcontent_id-pa11y_json-badge_html-wcag_level-error_count-warning_count-notice_count-connnone}

Store the latest accessibility result for a page in the database.

\textbf{Parameters} - \texttt{content\_id} (int): Content ID for the
page. - \texttt{pa11y\_json} (list{[}dict{]}): Pa11y results. -
\texttt{badge\_html} (str): Badge HTML markup. - \texttt{wcag\_level}
(str): WCAG level. - \texttt{error\_count}, \texttt{warning\_count},
\texttt{notice\_count} (int): Issue counts. - \texttt{conn}
(sqlite3.Connection): Database connection.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{generate\_badge\_html(wcag\_level, error\_count,
logo\_info,
report\_link)}\label{generate_badge_htmlwcag_level-error_count-logo_info-report_link}

Generate badge HTML for a given WCAG level and error count.

\textbf{Parameters} - \texttt{wcag\_level} (str): WCAG level. -
\texttt{error\_count} (int): Number of errors. - \texttt{logo\_info}
(dict): Mapping of WCAG levels to badge/logo URLs. -
\texttt{report\_link} (str): Link to the accessibility report.

\textbf{Returns} - \texttt{str}: Badge HTML markup.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{inject\_badge\_into\_html(html\_path, badge\_html,
report\_link,
logo\_info)}\label{inject_badge_into_htmlhtml_path-badge_html-report_link-logo_info}

Inject the badge/button into the HTML file after
\texttt{\textless{}main\textgreater{}}.

\textbf{Parameters} - \texttt{html\_path} (str): Path to the HTML file.
- \texttt{badge\_html} (str): Badge HTML markup. - \texttt{report\_link}
(str): Link to the accessibility report. - \texttt{logo\_info} (dict):
Badge/logo info.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{generate\_nav\_menu(context)}\label{generate_nav_menucontext}

Generate top-level navigation menu items from the content database.

\textbf{Parameters} - \texttt{context} (dict): Context dict, should
include `rel\_path'.

\textbf{Returns} - \texttt{list{[}dict{]}}: List of menu item dicts:
\{`title': str, `link': str\}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{generate\_wcag\_report(html\_path, issues, badge\_html,
config)}\label{generate_wcag_reporthtml_path-issues-badge_html-config}

Generate a detailed HTML accessibility report for a file using Jinja2
templates.

\textbf{Parameters} - \texttt{html\_path} (str): Path to the HTML file.
- \texttt{issues} (list{[}dict{]}): Pa11y issues. - \texttt{badge\_html}
(str): Badge HTML markup. - \texttt{config} (dict): Page and site
config.

\textbf{Returns} - \texttt{str}: Path to the generated report file.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{process\_all\_html\_files(build\_dir=`build',
config\_file=None,
db\_path=`db/sqlite.db')}\label{process_all_html_filesbuild_dirbuild-config_filenone-db_pathdbsqlite.db}

Process all HTML files in the build directory: - Run Pa11y checks -
Store results in DB - Generate badges and reports - Inject badges into
HTML - Copy changed files to docs/

\textbf{Parameters} - \texttt{build\_dir} (str): Build directory. -
\texttt{config\_file} (str, optional): Pa11y config file. -
\texttt{db\_path} (str): Path to SQLite database.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{copy\_to\_docs()}\label{copy_to_docs}

Copy all changed files from build/ to docs/.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{main()}\label{main}

CLI entry point. Parses arguments, runs checks, stores results, and
generates reports as needed.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Logging}\label{logging}

All major operations and errors are logged to \texttt{log/pa11y.log} for
debugging and auditing.

\subsection{Error Handling}\label{error-handling}

Robust error handling is implemented for subprocess calls, file I/O,
database operations, and template rendering. All failures are logged
with context.

\subsection{Example Usage}\label{example-usage}

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ oerforge }\ImportTok{import}\NormalTok{ verify}
\NormalTok{verify.process\_all\_html\_files()}
\end{Highlighting}
\end{Shaded}

\subsection{See Also}\label{see-also}

\begin{itemize}
\tightlist
\item
  \href{https://pa11y.org/}{Pa11y Documentation}
\item
  \href{https://www.w3.org/WAI/standards-guidelines/wcag/}{WCAG
  Guidelines}
\item
  \href{https://jinja.palletsprojects.com/}{Jinja2 Templates}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{License}\label{license}

See LICENSE in the project root.
