\section{About the Open Physics Education
Network}\label{about-the-open-physics-education-network}

Open Physics Ed is a collaborative, open-source initiative dedicated to
creating accessible, high-quality, and modern educational resources for
physics and computational science. Our mission is to lower barriers to
learning by providing free, open, and adaptable materials for students,
educators, and lifelong learners everywhere.

\subsection{Our Mission}\label{our-mission}

\begin{itemize}
\tightlist
\item
  \textbf{Accessibility:} We are committed to making all resources
  usable by everyone, including those with disabilities, and available
  in a variety of formats (HTML, PDF, Markdown, LaTeX, Jupyter, and
  more).
\item
  \textbf{Openness:} All materials are open source and free to use,
  modify, and distribute. We believe in challenging the corporate
  control of educational resources and supporting equitable access for
  all.
\item
  \textbf{Collaboration:} Anyone can contribute---students, educators,
  developers, and the broader community. Pull requests and suggestions
  are always welcome.
\item
  \textbf{Simplicity:} Our sites and materials are intentionally simple,
  plain, and easy to use, modify, and distribute. This ensures broad
  compatibility and accessibility.
\end{itemize}

\subsection{Who We Are}\label{who-we-are}

Open Physics Ed is organized by \href{https://dannycab.github.io/}{Danny
Caballero}, a professor of physics and computational science at Michigan
State University, with contributions from students, colleagues, and the
wider open education community. The project is inspired by years of
teaching, learning, and collaborating with others who share a passion
for open, equitable education.

\subsection{Our Projects}\label{our-projects}

\begin{itemize}
\tightlist
\item
  \textbf{Modern Classical Mechanics:} The first major course site in
  the Open Physics Ed family, providing interactive, accessible
  resources for teaching and learning classical mechanics.
  \href{https://dannycaballero.info/modern-classical-mechanics/}{Visit
  Modern Classical Mechanics}
\item
  \textbf{Future Courses:} Open Physics Ed is designed to organize and
  support efforts across many classes and topics. Modern Classical
  Mechanics is just the beginning---more courses and resources are
  coming soon.
\end{itemize}

\subsection{Philosophy \& Design
Principles}\label{philosophy-design-principles}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Everything is open source and free.}
\item
  \textbf{Accessibility is a priority:} We follow best practices and
  continually improve to meet WCAG and other standards.
\item
  \textbf{Anyone can contribute:} Suggest changes, add content, or
  improve materials---your input is valued.
\item
  \textbf{Simple, semantic, and accessible design:} We use semantic
  HTML, ARIA roles, and keyboard navigation to ensure usability for all.
\end{enumerate}

\subsection{Accessibility Commitments}\label{accessibility-commitments}

\begin{itemize}
\tightlist
\item
  Ongoing work to ensure all materials are accessible and usable by
  people with disabilities
\item
  Keyboard navigation and screen reader compatibility
\item
  High color contrast and readable font sizes
\item
  Descriptive alt text and link text
\item
  Open build process and documentation for contributors
\end{itemize}

\subsection{How to Contribute}\label{how-to-contribute}

We welcome contributions from anyone interested in improving open
physics education: - Suggest new content or improvements - Report issues
or bugs - Review or submit pull requests - Add new activities,
simulations, or resources - Help improve accessibility and design

You can contribute by creating an issue or pull request on our
\href{https://github.com/open-physics-ed/open-physics-ed-org.github.io}{GitHub
repository}.

\subsection{Contact \& Community}\label{contact-community}

\begin{itemize}
\tightlist
\item
  \href{https://github.com/dannycab}{Danny Caballero on GitHub}
\item
  \href{https://dannycaballero.info/modern-classical-mechanics/}{Modern
  Classical Mechanics}
\item
  \href{mailto:danny@hellmo.space}{Email}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Open Physics Ed is open source and always evolving. Join us in building
a more accessible, equitable future for physics education.
