\section{Activities}\label{activities}

Welcome to the activities page! Here you'll find interactive and
hands-on exercises to deepen your understanding of modern classical
mechanics.

\subsection{Sample Activity: Pendulum
Lab}\label{sample-activity-pendulum-lab}

\begin{itemize}
\tightlist
\item
  \textbf{Objective:} Explore the motion of a simple pendulum and
  measure its period.
\item
  \textbf{Materials:} String, weight, stopwatch, ruler.
\item
  \textbf{Instructions:}

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    Set up a pendulum of known length.
  \item
    Displace it by a small angle and release.
  \item
    Measure the time for 10 oscillations.
  \item
    Calculate the period and compare with theory.
  \end{enumerate}
\end{itemize}

\begin{quote}
\textbf{Tip:} Try different lengths and plot period vs.~length!
\end{quote}

\subsection{Sample Activity: Energy Skate Park
(PhET)}\label{sample-activity-energy-skate-park-phet}

\begin{itemize}
\tightlist
\item
  \textbf{Objective:} Investigate conservation of energy using a virtual
  skate park.
\item
  \textbf{Link:}
  \href{https://phet.colorado.edu/en/simulation/energy-skate-park}{PhET
  Energy Skate Park}
\item
  \textbf{Instructions:}

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    Open the simulation and build a track.
  \item
    Observe kinetic and potential energy as the skater moves.
  \item
    Experiment with friction and track shapes.
  \end{enumerate}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Add your own activities in \texttt{activities.md} using markdown!
